Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
Should be parencite, not in text.
"In certain circumstances" instead of "sometimes"

Tor bridges, intended as a way to get censored users access to Tor are easily
identified. They are also vulnerable to clogging attacks which make bridge
operators more easily identified \textcite{McLachlan:2009p197}.

@@

While Tor has been the subject of much academic literature, the primary
objective of researchers has historically been the attempt to reveal participant
identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
have been somewhat academic in nature and not necessarily feasible in practice
\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
the Tor network, supplying hostile data to Tor users or complicated knowledge of
usage patterns and an excess of patience. The technique demonstrated in this
paper is a low cost technique, which does not require very sophisticated
equipment and can be completed by a passive observer.

>>>>

Tor bridges, intended as a way to get censored users access to Tor are easily
identified. They are also vulnerable to clogging attacks which make bridge
operators more easily identified \parencite{McLachlan:2009p197}.

@@

While Tor has been the subject of much academic literature, the primary
objective of researchers has historically been the attempt to reveal participant
identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
have been somewhat academic in nature and not necessarily feasible in practice
\parencite{Raccoon:2008fk}. In certain circumstances they require compromise of
large parts of the Tor network, supplying hostile data to Tor users or
complicated knowledge of usage patterns and an excess of patience. The
technique demonstrated in this paper is a low cost technique, which does not
require sophisticated equipment and can be completed by a passive observer.
